\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2014-12-31 Report/project_report.tex
Minor fixes

Table \ref{tab:rmse_nees} provides summary statistics of each algorithm's performance on the synthetic datasets.
As expected from Figure \ref{fig:comp_3}, the SWF outperforms the MSCKF in terms of average RMSE on both rotation estimation and position estimation.
It is worth noting, however, that, on average, the MSCKF achieves low Normalized Estimation Error Squared (NEES) values, which indicates that the filter scores well on consistency if not on accuracy.
The average NEES values for the SWF are substantially higher because the SWF treats each window independently and has no built-in mechanism for propagating uncertainty from window to window (\cite{Sibley:2010:JFR} describes the proper procedure of using marginalization of old poses, which was not implemented in this work).
The accumulated drift error in the SWF quickly escapes the estimator's reported uncertainty envelope, and so this form of the SWF may be considered inconsistent in the absence of a known map.

@@

\begin{table}
    \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of IMU integration, MSCKF, and SWF on synthetic datasets.}
    \begin{threeparttable}
    \begin{tabular}{llccc} 
                    &                   & \multicolumn{3}{c}{Feature Count} \B      \\ \cline{3-5}
                    &                   & 40        & 60        & 100       \T\B    \\ \hline
        IMU Only    & Position ARMSE    & 0.3679    & 0.3679    & 0.3679    \T      \\
                    & Rotation ARMSE    & 0.1452    & 0.1452    & 0.1452            \\
                    & ANEES             & 0.2850    & 0.2850    & 0.2850            \\
                    & Compute Time\tnote{\dag}      & 8.90 s    & 8.90 s    & 8.90 s    \B      \\ \hline
        MSCKF       & Position ARMSE    & 0.2672    & 0.2550    & 0.2304    \T      \\
                    & Rotation ARMSE    & 0.1378    & 0.1247    & 0.0952            \\
                    & ANEES             & 10.18     & 12.03     & 16.76             \\
                    & Compute Time\tnote{\dag}     & 12.19 s   & 14.64 s   & 20.58 s   \B      \\ \hline
        SWF         & Position ARMSE    & 0.1750    & 0.1687    & 0.1755    \T      \\
                    & Rotation ARMSE    & 0.0495    & 0.0377    & 0.0481            \\
                    & ANEES             & 2280      & 2093      & 2013              \\
                    & Compute Time\tnote{\dag}     & 114.3 s   & 175.9 s   & 245.3 s   \B      \\ \hline
    \end{tabular}
    \begin{tablenotes}
        \item [\dag] Running MATLAB 2014b on a MacBook Pro Retina (11,3) with a 2.3GHz Intel Core i7 processor and 16 GB of DDR3L RAM.
    \end{tablenotes}
    \end{threeparttable}
    \label{tab:rmse_nees}
\end{table}

>>>>

Table \ref{tab:rmse_nees} provides summary statistics of each algorithm's performance on the synthetic datasets.
As expected from Figure \ref{fig:comp_3}, the SWF outperforms the MSCKF in terms of average RMSE on both rotation estimation and position estimation.
It is worth noting, however, that, on average, the MSCKF achieves low Normalized Estimation Error Squared (NEES) values, which indicates that the filter scores well on consistency if not on accuracy.
The average NEES values for the SWF are substantially higher because the SWF treats each window independently and has no built-in mechanism for propagating uncertainty from window to window (\cite{Sibley:2010:JFR} describes how this can be remedied by marginalizing old poses, a technique which was not implemented in this work).
The accumulated drift error in the SWF quickly escapes the estimator's reported uncertainty envelope, and so this form of the SWF may be considered inconsistent in the absence of a known map.

@@

\begin{table}
    \centering
    \caption{Comparison of Average Root Mean Squared Error (ARMSE), Average Normalized Estimation Error Squared (ANEES), and Compute Time of IMU integration, MSCKF, and SWF on synthetic datasets for the interval $k\in[1215,1715]$.}
    \begin{threeparttable}
    \begin{tabular}{llccc} 
                    &                   & \multicolumn{3}{c}{Feature Count} \B      \\ \cline{3-5}
                    &                   & 40        & 60        & 100       \T\B    \\ \hline
        IMU Only    & Position ARMSE    & 0.3679    & 0.3679    & 0.3679    \T      \\
                    & Rotation ARMSE    & 0.1452    & 0.1452    & 0.1452            \\
                    & ANEES             & 0.2850    & 0.2850    & 0.2850            \\
                    & Compute Time\tnote{\dag}      & 8.90 s    & 8.90 s    & 8.90 s    \B      \\ \hline
        MSCKF       & Position ARMSE    & 0.2672    & 0.2550    & 0.2304    \T      \\
                    & Rotation ARMSE    & 0.1378    & 0.1247    & 0.0952            \\
                    & ANEES             & 10.18     & 12.03     & 16.76             \\
                    & Compute Time\tnote{\dag}     & 12.19 s   & 14.64 s   & 20.58 s   \B      \\ \hline
        SWF (25 Poses)         & Position ARMSE    & 0.1750    & 0.1687    & 0.1755    \T      \\
                    & Rotation ARMSE    & 0.0495    & 0.0377    & 0.0481            \\
                    & ANEES             & 2280      & 2093      & 2013              \\
                    & Compute Time\tnote{\dag}     & 114.3 s   & 175.9 s   & 245.3 s   \B      \\ \hline
    \end{tabular}
    \begin{tablenotes}
        \item [\dag] Running MATLAB 2014b on a MacBook Pro Retina (11,3) with a 2.3GHz Intel Core i7 processor and 16 GB of DDR3L RAM.
    \end{tablenotes}
    \end{threeparttable}
    \label{tab:rmse_nees}
\end{table}
